Spoken Corpus of Karel Mako\v{n}

### 2018-04-14 2018-clarin-pisa/makon-data.tex
clarin2018: expanded abstract

\begin{document}
\maketitle
\begin{abstract}
  We present the spoken corpus of Karel Mako\v{n}. This paper
  briefly outlines the system for processing the corpus, which has been
  published in a previous work, and elaborates on the corpus. A baseline for
  topical analysis is presented.
\end{abstract}

>>>>

\begin{document}
\maketitle
\begin{abstract}
  We present the spoken corpus of Karel Mako\v{n}, a corpus of spontaneous
  speech by a single speaker in Czech language within the domain of Christian
  mystic, with partly automatic, partly manual transcription obtained through a
  web application made for correcting the output of ASR.
  This paper briefly outlines the system for processing the corpus and
  elaborates on the corpus itself. A baseline for topical analysis is presented.
\end{abstract}
